---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Discriminant-Analysis-k-Nearest-Neighbors

The head of the zone  of a banking entity has five offices under his command. 

The type variable indicates the group in which each individual is classified: a-office manager, b-commercial managers, c-controllers.

The rest of the variables are the sales in the last month of each of these workers under his command are in: sales of life insurance, sales of payroll accounts, sales of virtual cards and sales of credit cards. He wanted to know if the individuals are well classified in their position (director -a-, manager -b- or controller -c-) based on their sales or should we change someone, promoting or demoting them.

We will classify individuals according to the k=3 nearest neighbors method and the k=3 nearest neighbors method with cross validation.

## 1. k=3 nearest neighbors method

```{r , echo = FALSE,warning=FALSE,message=FALSE}
insurance<-c(2,3,3,2,4,4,6,5,6,6,
           7,6,5,5,7,8,7,8,8,7)
accounts<-c(2,2,3,3,3,5,6,5,
           7,6,7,8,6,3,9,9,5,9,2,2)
virtual<-c(3,3,4,4,3,4,5,5,6,6,
             5,5,6,3,7,7,6,8,8,7)
credits<-c(3,3,3,4,3,3,5,5,5,6,
           5,5,5,4,7,7,5,8,7,8)
tipo<-c("a"," a" ,"a" ,"a" ,"a" ,"b" ,"b" ,"b", "b" ,"b" ,"b" ,"b" ,"b" ,"b" ,"c" ,"c" ,"c" ,"c" ,"c" ,"c")
datos<-matrix(c(insurance,accounts,virtual,credits),ncol=4)
colnames(datos)<-c("insurance","accounts","virtual","credits")
datos
library(MASS)
datos.lda<-lda(datos,tipo)
datos.lda
datos.lda$scaling
plot(datos.lda)
clasif<-predict(datos.lda)$class
clasif
errorrate<- 1-sum(clasif==tipo)/ 20
errorrate

```

## 2. k=3 nearest neighbors method with cross validation 

```{r , echo = FALSE,warning=FALSE,message=FALSE}

tipo<-c("a"," a" ,"a" ,"b" ,"b" ,"b" ,"b" ,"b", "b" ,"b" ,"c" ,"c" ,"c" ,"c" ,"c" ,"d" ,"d" ,"d" ,"d" ,"d")

#CRUZADA
clasif.cv<-lda(datos,tipo,CV=T)$class
clasif.cv
errorratecv<- 1-sum(clasif.cv==tipo)/20
errorratecv

#K VECINOS MÁS PROXIMOS 
library(class)
datos.k2<-knn(datos,datos,tipo,3)
datos.k2
errorratek2<- 1-sum(datos.k2==tipo)/20
errorratek2

#MÉTODO DE LOS K VECINOS MÁS PRÓXIMOS. VALIDACIÓN CRUZADA
datos.k2vc<-knn.cv(datos,tipo,3)
datos.k2vc
errorrate.k2vc <- 1-sum(datos.k2vc==tipo)/20
errorrate.k2vc

tipo<-c("a"," a" ,"a" ,"b" ,"b" ,"b" ,"b" ,"b", "b" ,"b" ,"c" ,"c" ,"c" ,"c" ,"c" ,"d" ,"d" ,"d" ,"d" ,"d")

#CRUZADA
clasif.cv<-lda(datos,tipo,CV=T)$class
clasif.cv
errorratecv<- 1-sum(clasif.cv==tipo)/20
errorratecv

#K VECINOS MÁS PROXIMOS 
library(class)
datos.k2<-knn(datos,datos,tipo,3)
datos.k2
errorratek2<- 1-sum(datos.k2==tipo)/20
errorratek2

#MÉTODO DE LOS K VECINOS MÁS PRÓXIMOS. VALIDACIÓN CRUZADA
datos.k2vc<-knn.cv(datos,tipo,3)
datos.k2vc
errorrate.k2vc <- 1-sum(datos.k2vc==tipo)/20
errorrate.k2vc

```
By performing the k=3 nearest neighbors method and the k=3 nearest neighbors method with cross validation. The results indicate that there are more elements misclassified and that the error rate increases, so this result would not be very significant, and that it could probably be classified into 4 groups according to the results of the validations.
